\begin{abstract}
We provide a deterministic polynomial-time algorithm that, for a given $k$-uniform hypergraph $H$ with $n$ vertices and edge density $d$,
finds a complete $k$-partite subgraph of $H$ with parts of size at least ${c(d, k)(\log n)^{1/(k-1)}}$.
This generalizes work by Mubayi and Tur\'{a}n on bipartite graphs.
The value we obtain for the part size matches the order of magnitude guaranteed by the non-constructive proof due to
Erd\H{o}s and is tight up to a constant factor.
\end{abstract}

\maketitle


\section{Introduction}\label{sec:introduction}

Hypergraph Tur\'{a}n problems concern how many edges a $k$-uniform hypergraph $H = (V, E)$ with $n$ vertices can have without containing a specific subgraph $G$.
The maximal such number is known as the \emph{Tur\'{a}n number} $\ex{n}{G}$.
It is known~\cite{keevash2011hypergraph}
that $\ex{n}{G}$ is sublinear in $\binom{n}{k}$ if and only if $G$ is $k$-partite, i.e.,
if its vertex set can be partitioned into $k$ disjoint sets such that each edge contains exactly one vertex from each part.
Kőv\'{a}ri, S\'{o}s, and Tur\'{a}n~\cite{Kovari1954} (for $k=2$) and
Erd\H{o}s~\cite{Erdos1964} (for any $k \geq 2$) established that
\[ \label{eq:erdos64-intro}
    \ex{n}{\compoverset{k}{t}} \leq \binom{n}{k} \cdot n^{-\frac{1}{t^{(k-1)}}}\,.
\]
This result implies the following.

\begin{remark} \label{rk:order}
    If $H$ is a $k$-graph with at least $d \binom{n}{k}$ edges for some constant $d > 0$, then it contains $\compoverset{k}{t}$
    as a subgraph, with $t = c(d, k) (\log(n))^{1/(k-1)}$.
\end{remark}

Furthermore, the order of magnitude of $t$ is tight up to a constant factor:
For some constant $\hat{c}(d, k) > 0$,
there are $k$-graphs with $n$ vertices and edge density
$d$ that do not contain $\compoverset{k}{\hat{t}}$ as a subgraph, where
$\hat{t} = \hat{c}(d, k)\log(n)^{1/(k-1)}$.
This was already noted by Erd\H{o}s~\cite{Erdos1964} and can be proved via the random alteration method~\cite{alon2016probabilistic}.


Due to the fundamental role of Erd\H{o}s' result,
it is natural to ask whether a fast search algorithm for a complete $k$-partite subgraph of the size stated in Remark~\ref{rk:order} exists.
A brute-force search for a $\compoverset{k}{t}$ would involve checking all $\binom{n}{kt}$ vertex subsets, which is superpolynomial in $n$ for ${t = \bigOmega{(\log n)^{1/(k-1)}}}$.
For $k=2$, Mubayi and Tur\'{a}n~\cite{MUBAYI2010174} developed a deterministic polynomial-time algorithm which reaches the stated order of magnitude for the subgraph part size.
This work extends their approach to the general case of $k$-uniform hypergraphs, reaching analogous results for $k \ge 3$.
More concretely, we prove the following.

\begin{theorem} \label{thm:main_theorem}
There is a deterministic algorithm that, given a $k$-graph $H$ with $n$ vertices and $m=d \binom{n}{k}$ edges, finds a complete balanced $k$-partite subgraph $\compoverset{k}{t}$ in polynomial time, where
\[
    t = t(n, d, k) = \left\lfloor \left( \frac{\log n}{\log (16/d)}  \right)^{\frac{1}{k-1}} \right \rfloor \,.
\]
\end{theorem}
This value of $t$ matches the order of magnitude from Remark~\ref{rk:order}.

\section{The algorithm}\label{sec:finding-a-balanced-$k$-partite-subgraph}

We present a recursive algorithm, \texttt{FindPartite}, that finds a $\compoverset{k}{t}$ in a given $k$-graph $H$.
The core idea is to reduce the uniformity of the problem from $k$ to $k-1$ in each recursive step.
The algorithm takes a $k$-graph $H$ with $n$ vertices and $m$ edges as input.
It first defines the target part size $t$, a small set size $w$,
and a threshold edge count $s$ for the recursive call, based on the input hypergraph's parameters:
\begin{align*}
    t &= t(n, d, k) = \left\lfloor \left( \frac{\log n}{\log (16/d)}  \right)^{\frac{1}{k-1}} \right \rfloor\,, \\
    w &= w(n, d, k) = \left\lceil \frac{4 t}{d} \right\rceil\,, \text{ and } \\
    s &= s(n, d, k) = \left\lceil \left( \frac{d}{4} \right)^t \binom{n}{k-1} \right\rceil\,,
\end{align*}
where $d = \frac{m}{\binom{n}{k}}$ is the edge density of $H$.
The main steps are:
\begin{enumerate}
    \item \textbf{Base Case ($k=1$):} The edge set of a 1-graph is just a collection of singleton sets of vertices.
    Return the set of all vertices that are ``edges''.

    \item \textbf{Select High-Degree Vertices:} Choose a set $W \subset V$ of $w$ vertices with the highest degrees in~$H$. \label{W}

    \item \textbf{Find a Dense Link Graph:} Iterate through all $t$-subsets $T \subset W$.
    For each $T$, consider the set $S$ of all $(k-1)$-subsets of $V$ that form a hyperedge with \emph{every} vertex in $T$. \label{link}

    \item \textbf{Recurse:} As we prove further along using the Kőv\'{a}ri–S\'{o}s–Tur\'{a}n theorem, for at least one choice of $T$,
    the resulting set $S$ is large ($|S| \ge s$). We form a new $(k-1)$-graph $H'=(V, S)$ and make a recursive call: \texttt{FindPartite($H'$, $k-1$)}.

    \item \textbf{Construct Solution:} The recursive call returns $k-1$ parts $V_1, \dots, V_{k-1}$ of size at least $t$.
    By construction, every choice of vertices from these parts forms an edge in $H'$ with every vertex of $T$.
    Thus, $(V_1, \dots, V_{k-1}, T)$ form the desired $\compoverset{k}{t}$ in the original graph $H$.

\end{enumerate}

The pseudocode is given in Algorithm~\ref{alg:kpartite}.

\begin{algorithm}[H]
    \caption{Finding a balanced partite $k$-graph}
    \label{alg:kpartite}
    \begin{algorithmic}[1]
        \Function{FindPartite}{$H, k$}
            \If {$k = 1$}
                \State \Return $(\{x \colon \{x\} \in E(H)\})$
            \EndIf

            \State $n \gets |V(H)|$, $m \gets |E(H)|$, $d \gets \frac{m}{\binom{n}{k}}$
            \State $t \gets t(n, d, k)$, $w \gets w(n, d, k)$, $s \gets s(n, d, k)$
            \State \textbf{assert} $t \ge 2$

            \State $W \gets$ a set of $w$ vertices with highest degree in $H$
            \ForAll{$T \in \binom{W}{t}$}
                \State $S \gets \{\,y \in \binom{V}{k-1} \colon \forall x \in T, \{x\} \cup y \in E(H)\,\}$
                \If{$|S| \ge s$}
                    \State $H' \gets (V, S)$  \Comment{$H'$ is a $(k-1)$-graph}
                    \State $(V_1, \dots, V_{k-1}) \gets$ \Call{FindPartite}{$H', k-1$} \label{recurse}
                    \State \Return $(V_1, \dots, V_{k-1}, T)$
                \EndIf
            \EndFor
        \EndFunction
    \end{algorithmic}
\end{algorithm}
\newpage

\section{Proof of correctness}\label{sec:correctness}

We now present the proof that Algorithm~\ref{alg:kpartite} is correct in the sense that
all the steps are well-defined and that it returns a tuple $(V_1, \dots, V_k)$ of disjoint sets $V_i \subset V(H)$
of size at least $t$ spanning a complete $k$-partite subgraph in $H$.
We assume $t \ge 2$ for our estimates to be easier.
If $t < 2$, we may just return the vertices of any single edge in $H$.

It is not immediately clear that the set $W$ defined in step~\ref{W} of the algorithm
is well-defined, as for this it is necessary that $w \leq n$.
To show this, we first observe that our assumption $t \geq 2$
implies that $ 1 \geq d \geq \frac{16}{\sqrt{n}}$.
Suppose, by way of contradiction, that $w > n$.
Then, we have
\[
    n \leq w - 1 \leq \frac{4t}{d} \leq \frac{4\log n}{d\log(16/d)} \leq \frac{4 \sqrt{n} \log n }{16 \log(16/d)}\,.
\]
Taking the logarithms to be in base $e$, we note that $\log x \leq \sqrt{x}$ for all positive $x$,
and that $\log(16/d) > 1$.
Therefore, we get $n < \frac{n}{4}$, which is a contradiction.

Next, we prove that in step~\ref{link} of the algorithm
we indeed find a set $T \in \binom{W}{t}$ such that the associated set
$S \subset \binom{V}{k-1}$ has size at least $s$.
That is, Algorithm~\ref{alg:kpartite} reaches line~\ref{recurse} at some point in the for loop.
For this, consider the bipartite graph $B$ with parts $\binom{V}{k-1}$ and $W$ with edge set
\[
  \left\{(x, y) \in \binom{V}{k-1} \times W \middle| \, x \cup \{y\} \in E \right\}\,.
\]
The edges of $B$ correspond to the edges containing each vertex in $W$, so there are
\[
    z = \sum_{y \in W} d_H(y) \geq k \cdot m \cdot \frac{w}{n} = \frac{k \cdot w \cdot d \cdot \binom{n}{k}}{n} = w \cdot d \cdot \binom{n - 1}{k-1}
\]
of them, where the inequality follows from the fact that we have picked a set of $w$ vertices with highest degree in $H$.
The existence of a set $T \subset W$ as desired is equivalent to there being $T \subset W$ of size $t$ and a set $S \subset \binom{V}{k-1}$ of size $s$
such that the induced bipartite subgraph $B[S, T]$ is complete.
To prove that this is the case,
we use the following version~\cite{Hylten1958} of the Kőv\'{a}ri–S\'{o}s–Tur\'{a}n theorem~\cite{Kovari1954}.

\begin{lemma}\label{thm:kst}
    Let $u, w, s, t$ be positive integers with $u \geq s$, $w \geq t$, and let $B$ be a bipartite graph with parts $W$ and $U$ such that
    $|U| = u, |W| = w$.
    If $B$ has more than \[(s - 1)^{1 / t}(w - t + 1)u^{1 - 1 / t} + (t - 1)u\] edges, then there are
    $T \subset W$ of size $t$ and $S \subset U$ of size $s$ such that the induced bipartite subgraph $B[S, T]$ is complete.
\end{lemma}

We apply the lemma with $u = \binom{n}{k-1}$.
It is clear from the definitions that our parameter satisfy the requirements $u \geq s$ and $w \geq t$.
Suppose, by way of contradiction, that
\[
    w \cdot d \cdot \binom{n - 1}{k-1} \leq (s - 1)^{1 / t}(w - t + 1)\binom{n}{k-1}^{1 - 1 / t} + (t - 1)\binom{n}{k-1}\,.
\]
Dividing by $\binom{n}{k-1}$ then shows that
\[
    \frac{1}{2} \cdot w \cdot d
    \leq \left( 1 - \frac{k-1}{n}\right) \cdot w \cdot d
    = w \cdot d \cdot \frac{\binom{n-1}{k-1}}{\binom{n}{k-1}}
    < w \left( \frac{s-1}{\binom{n}{k-1} } \right)^{1 / t} + (t - 1)\,,
\]
where the first inequality follows from $n \geq 16^{2^{k-1}} > 2(k-1)$, which follows from $t \geq 2$ and $d \leq 1$.
Finally, since $t \leq \frac{w \cdot d}{4}$ by the definition of $w$, we obtain
\[
    \left( \frac{d}{4}\right)^t \binom{n}{k-1} < s-1\,,
\]
in contradiction to the definition of $s$.
So far, we have shown that the sets defined in Algorithm~\ref{alg:kpartite}
are well-defined and that the recursive call in line~\ref{recurse} is reached.
We are now ready to prove that the algorithm returns a $\compoverset{k}{t}$
by examining what happens in the recursive call.
More precisely, we show the following.

\begin{theorem}
    For $k \geq 2$, if $t \geq 2$, Algorithm~\ref{alg:kpartite} returns a tuple $(V_1, \dots, V_k)$ of disjoint sets $V_i \subset V(H)$ such that
    $|V_i| \geq t$ and $H[V_1, \dots, V_k]$ is complete.

    \begin{proof}
        We proceed by induction on $k$.
        For $k=2$, the recursive call returns the common neighborhood $V_1$ of the vertices in $T$,
        which is obviously disjoint from $T$, so it only remains to check that $|V_1| \geq t$.
        Now, since by construction $|V_1| = |S| \geq s$, it is enough that
        \[
            s
            = \left\lceil \left( \frac{d}{4} \right)^t \cdot n \right\rceil
            \geq \left( \frac{d}{4} \right)^{\frac{\log n}{\log(16/d)}}  \cdot n
            = \left( 4 \cdot \frac{d}{16} \right)^{\frac{\log n}{\log(16/d)}} \cdot n
            = \frac{1}{n} \cdot 4^{\frac{\log n}{\log(16/d)}} \cdot n
            \geq 4^t
            > t\,.
        \]

        For $k \geq 3$, we assume the inductive hypothesis holds for $k-1$.
        If $d'$ is the edge density of the $(k-1)$-graph $H'$
        and $t' = t(n, d', k-1)$, as long as $t' \geq 2$, the recursive call returns
        a tuple $(V_1, \dots, V_{k-1})$ of disjoint sets $V_i \subset V(H)$ such that
        $|V_i| \geq t'$ and $H'[V_1, \dots, V_{k-1}]$ is complete.

        We claim that $t' \geq t$.
        This implies that $t' \geq 2$ so we get to apply the inductive hypothesis to $H'$.
        Furthermore, the sets $V_i$ that we obtain when applying the algorithm to $H'$
        are of size at least $t' \geq t$.
        By construction of $S$, all the edges in $H'$ are disjoint from $T$,
        and therefore so are the sets $V_i$.
        This means that the sets $V_1, \dots, V_{k-1}, T$ are disjoint.
        In addition, for all $(x_1, \dots x_{k-1}, y) \in V_1 \times \dots \times V_{k-1} \times T$,
        we have that $\{x_1, \dots, x_{k-1}\} \in S$ so $\{x_1, \dots, x_{k-1}, y\} \in E(H)$.
        Equivalently, $H[V_1, \dots, V_{k-1}, T]$ is complete, finishing the proof.

        Let us now prove the claim that $t' \geq t$.
        By the definition of $s$, we have $d' \geq \left( \frac{d}{4} \right)^t$.
        Therefore,
        \[
            t' \geq
            %
            \left\lfloor \left(  \frac{\log n}{\log \left(\frac{16}{(d/4)^t}\right)} \right)^
            {\frac{1}{k-2}} \right\rfloor \geq
            %
            \left\lfloor \left(  \frac{\log n}{\log 16 - t \log (d/4)} \right)^
            {\frac{1}{k-2}} \right\rfloor\,.
        \]
        Then, we substitute the definition of $t$, where removing the floor function
        maintains the inequality because the right side is decreasing in $t$ (recall $d \leq 1$):
        \begin{equation*}
            t' \geq
            %
            \left\lfloor \left(  \frac{\log n}
            {\log 16 - \left(  \frac{\log n}{\log (16/d)} \right)^{\frac{1}{k-1}}  \log (d/4)} \right)^
            {\frac{1}{k-2}} \right\rfloor
            =
            %
            \left\lfloor \left(  \frac{(\log n)^{\left(1-\frac{1}{k-1}\right)}}
            {\frac{\log 16}{(\log n)^{\frac{1}{k-1}}} - \frac{\log (d/4)}{\log (16/d)^{\frac{1}{k-1}}} }
            \right)^{\frac{1}{k-2}} \right\rfloor\,.
        \end{equation*}
        We claim that we bound the denominator by showing that
        \begin{equation} \label{eq:denominator_bound}
            \frac{\log 16}{(\log n)^{\frac{1}{k-1}}} - \frac{\log (d/4)}{\log (16/d)^{\frac{1}{k-1}}}
            \leq \left( \log (16/d) \right)^{\left( 1 - \frac{1}{k-1} \right)}\,.
        \end{equation}
        Then, the expression simplifies to
        \[
            t'
            %
            \geq \left\lfloor \left(  \frac{(\log n)^{\left(1-\frac{1}{k-1}\right)}}
            {\left( \log (16/d) \right)^{\left( 1 - \frac{1}{k-1} \right)}}
            \right)^{\frac{1}{k-2}} \right\rfloor
            %
            = \left\lfloor \left(  \frac{\log n}
            {\log (16/d)}
            \right)^{\frac{1}{k-2}\left( 1 - \frac{1}{k-1} \right)} \right\rfloor
            = \left\lfloor \left(  \frac{\log n}{\log (16/d)} \right)^{\frac{1}{k-1}} \right\rfloor
            = t\,,
        \]
        as desired.
        Let us prove Inequality~\eqref{eq:denominator_bound}.
        Suppose, by way of contradiction, that it does not hold.
        We can rewrite
        \[
            (\log (16/d))^{\left( 1 - \frac{1}{k-1} \right)}
            = \frac{\log (16/d)}{\log (16/d)^{\frac{1}{k-1}}}
        \]
        and rearrange the inequality to obtain
        \[
            \frac{\log 16}{(\log n)^{\frac{1}{k-1}}}
            > \frac{\log (16/d) + \log (d/4)}{\log (16/d)^{\frac{1}{k-1}}}
            = \frac{\log 4}{(\log (16/d))^{\frac{1}{k-1}}}\,.
        \]
        This implies that
        \[
            t
            \leq \left( \frac{\log n}{\log (16/d)} \right)^{\frac{1}{k-1}}
            < \frac{\log 16}{\log 4} = 2\,,
        \]
        which contradicts the assumption that $t \geq 2$.
    \end{proof}
\end{theorem}

\section{Proof of Polynomial Complexity}\label{sec:complexity}

We now analyze the computational complexity of Algorithm~\ref{alg:kpartite} to show that it runs in time polynomial in $n$ for any fixed uniformity $k$.
We consider the input hypergraph $H$ to be given as an adjacency $k$-dimensional tensor.
We make the assumption that we have a machine with arbitrarily large random-access memory,
and that the operations on integers and floating-point numbers take constant time.
Not making these assumptions would only add logarithmic factors to the running time, which we ignore for simplicity.

Let $T_k(n)$ denote the worst-case running time of the function \texttt{FindPartite} when called on a $k$-uniform hypergraph with $n$ vertices.
The algorithm's structure gives a recurrence relation for $T_k(n)$.
We first analyze the cost of the operations within a single call for a fixed $k$, excluding the recursive step.

Assuming that the input tensor consists of a flattened boolean array of size $n^k$,
querying whether a set of $k$ vertices forms an edge in $H$ can be done in constant time.
Therefore, calculating the number of edges $m$ can be done in $\bigO{n^k}$ time by iterating through all $\binom{n}{k}$ possible edges.
The parameters $n, m, d, t, w, s$ are computed in constant time after this step.

The set $W$ of $w$ vertices with highest degrees can be constructed in time $\bigO{n^k}$, by, for example,
creating an array with the degree of each vertex (in time  $\bigO{n \cdot n^{k-1}} = \bigO{n^k}$), sorting it (in time $\bigO{n \log n}$),
and taking the first $w$ elements.

The subsets of $t$ elements of $W$ can be iterated through in time $\bigO{\binom{w}{t}}$~\cite{reingold1977combinatorial}.
Similarly to the argument by Mubayi and Tur\'{a}n~\cite{MUBAYI2010174}, we can bound this quantity by a polynomial in $n$.
Indeed,
\[
    \binom{w}{t} \leq \left(\frac{ew}{t}\right)^t
    \leq \left(\frac{e(4t/d + 1)}{t}\right)^t
    \leq \left(\frac{4e}{d} + \frac{e}{2}  \right)^t
    \leq \left(\frac{4.5 \cdot e}{d}\right)^t < e^{t(2.6 + \log (1/d))}
    = e^{2.6 \cdot t} e^{\log (1/d) \cdot t}\,.
\]
For the first term, we use the fact that $t < (\log n)^{1/(k-1)} \leq \log n$
and so ${e^{2.6 \cdot t} < e^{2.6 \cdot \log n} = n^{2.6}}$.
For the second term, we use that $t < (\log(n)/\log(1/d))^{1/(k-1)} \leq \log(n)/\log(1/d)$,
so $e^{\log (1/d) \cdot t} < n$.
All in all, we have
\[
    \binom{w}{t} < n^{2.6} n = n^{3.6}\,.
\]
In each iteration of the loop, the set $S$ can be constructed in the following way.
We initialize a flattened boolean array $A$ of size $n^{k-1}$,
with all entries set to \texttt{true}.
We iterate through all $x \in \binom{[n]}{k-1}$ and $y \in T$
and set the entry corresponding to $x$ to \texttt{false} if $x \cup \{y\}$ is not an edge in $H$.
All in all, this takes $\bigO{tn^{k-1}} = \bigO{n^k}$ steps, and then counting the number of \texttt{true} entries in the array takes $\bigO{n^{k-1}}$ time.
Therefore, the for loop (with the recursive call) takes $\bigO{\binom{w}{t} n^{k}} = \bigO{n^{k+3.6}}$ time.

Finally, when the condition $|S| \geq s$ is satisfied, the recursive call to \texttt{FindPartite} is made.
We can pass the array $A$ to the recursive call directly, and the recursive call takes time $T_{k-1}(n)$.
Putting everything together, we have the recurrence relation $T_k(n) = T_{k-1}(n) + \bigO{n^{k+3.6}}$.
This, together with the base case $T_1(n) = \bigO{n}$, gives us $T_k(n) = \bigO{n^{k+3.6}}$.

\section{Conclusion and Future Work}\label{sec:conclusion-and-future-work}

We have presented a deterministic,
polynomial-time algorithm to find a large complete balanced $k$-partite subgraph in any sufficiently dense $k$-uniform hypergraph.
This provides a constructive counterpart to a classical existence result by Erd\H{o}s in extremal hypergraph theory.

Several avenues for future research remain open.
\begin{itemize}
    \item \textbf{General Blow-ups:} Our algorithm finds a blow-up of a single edge, $\compoverset{k}{t}$.
    Can this framework be adapted to find a $t$-blowup of an arbitrary fixed $k$-graph $G$ when its Tur\'{a}n density is exceeded by a positive constant?
    For example, for $k=2$, there are existence results for $t = \bigOmega{\log n}$~\cite{bollobas1973structure}, but directly adapting Algorithm~\ref{alg:kpartite} would only
    yield t = $\bigO{(\log n)^{1/(|V(G)| - 1)}}$.
    \item \textbf{Unbalanced k-Partite Graphs:} The algorithm could be modified to search for unbalanced complete partite graphs $\compdots{t_1}{t_k}$, where the part sizes may grow at different rates.
    \item \textbf{Optimality:} The bounds on $t$ are asymptotically tight, but the constants can likely be improved with a more refined analysis.
\end{itemize}

\subsection*{Acknowledgements}

The ideas in this work stem from the author's master's thesis of the same name,
Universitat Polit\`{e}cnica de Catalunya,
under the supervision of Richard Lang.
The author thanks him for suggesting the problem and for his guidance and support throughout the project.
